---
title: "CEHAT Air Quality App"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

EXAMPLE

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```



```{r highlow}
library(PurpleAirCEHAT)
library(dplyr)
library(tidyverse)
PAfull <- read.csv("C:/Users/jimzi/Downloads/pm25_2020_12_01T07_59_59_000Z_to_2021_01_01T08_00_00_000Z.csv")

PAfull <- PurpleAirCEHAT::cleanPA(PAfull)

PAhourly <- PurpleAirCEHAT::hourlyPA(PAfull)

PAhi_lo <- PurpleAirCEHAT::highslows(PAhourly)

sensors <- unique(PAfull[,c(5,4)])
#adding the names of 11 sensors
#to add another sensor, end the previous line with a comma, and input the following info for the new sensor:
#     longitude == -118.1965 & latitude == 33.93868 ~ "Sensor: CEHAT 8",
#     longitude == <longitude> & latitude == <latitude> ~ "<name>")


sensors <- mutate(sensors,
                  names = case_when(longitude == -118.1901 & latitude == 33.94106 ~ "Sensor: SCSG-14",
                                    longitude == -118.1953 & latitude == 33.94354 ~ "Sensor: CEHAT 7-CD",
                                    longitude == -118.2201 & latitude == 33.94178 ~ "Sensor: CEHAT-01",
                                    longitude == -118.1985 & latitude == 33.96063 ~ "Sensor: CEHAT 5",
                                    longitude == -118.2184 & latitude == 33.96757 ~ "Sensor: CCA Mountainview and Olive",
                                    longitude == -118.2146 & latitude == 33.95058 ~ "Sensor: CEHAT-St. Helens-STEM",
                                    longitude == -118.1685 & latitude == 33.93553 ~ "Sensor: SCSG_15",
                                    longitude == -118.1673 & latitude == 33.92019 ~ "Sensor: SCSG_20",
                                    longitude == -118.2225 & latitude == 33.95094 ~ "Sensor: CEHAT 7-SE",
                                    longitude == -118.1965 & latitude == 33.93868 ~ "Sensor: CEHAT 8",
                                    longitude == -118.2181 & latitude == 33.96192 ~ "Sensor: CEHAT 3")
)

wessy_pal <- c("high"="#C93312","low"="#899DA4")


inputPanel(
  selectInput("sensor", label = "View sensor:",
              choices = sensors$names, selected = "Sensor: SCSG-14"),
  
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20)
)



renderPlot({
  print(ggplot(data=PAhi_lo[PAhi_lo$names == input$sensor,], aes(x=day, y=PM2.5, group = day)) +
        geom_line(lwd=1)+
        geom_point(data=PAhi_lo[PAhi_lo$type == "high" & PAhi_lo$PM2.5<=300  & PAhi_lo$names == input$sensor, ], 
                 aes(x=day, y=PM2.5, group = type, col="high"), size=5)+
        geom_point(data=PAhi_lo[PAhi_lo$type == "low" & PAhi_lo$names == input$sensor, ], 
                 aes(x=day, y=PM2.5, group = type, col="low"), size=5)+
        scale_color_brewer(palette="Dark2")+
        labs(x = "Day", y = "PM2.5 (µg/m³)") +
        scale_colour_manual(name="Type",values=wessy_pal, guide = guide_legend(override.aes=aes(fill=NA)) ) +    scale_fill_manual(name="Type",values=wessy_pal) +
        ggtitle(input$sensor) +
        theme_minimal())
})

renderPlot({
  hist(PAhi_lo$PM2.5[PAhi_lo$names==input$sensor], probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "PM2.5 Value (µg/m³)", main = "High and Low Histogram")

})

```




